EUC_PVE

### 2014-07-23 markdowns/master.rmd
no code blocks

---
title: "EUV_PVE"
author: "Court Campany"
date: "Tuesday, July 22, 2014"
output: html_document
---

@@

```
seedling predawn and midday water potentials
```

@@

```
Modelled C gain versus harvest seedling total carbon
```

>>>>

---
title: "EUC_PVE"
author: "Court Campany"
date: "Tuesday, July 22, 2014"
output: html_document
---

@@

### seedling predawn and midday water potentials

@@

Modelled C gain versus harvest seedling total carbon
